\documentclass[onecolumn]{IEEEtran}
\usepackage{url,longtable}

\title{Books authored by C.P. Ravikumar}

\author{Updated on May 12, 2026}

\begin{document}
\maketitle 

\section*{Technical Books and Monographs}

\begin{longtable}{|l| p{2cm} | p{5cm} | p{2cm}|p{1cm}|}
\hline
No & Author & Title   & Publisher     & Year \\
\hline
1        & 
C.P. Ravikumar  & 
Parallel Methods for VLSI Layout Design \footnote{ \url{http://www.amazon.com} for details. A review of the book appeared in IEEE Concurrency - see \url{https://ieeexplore.ieee.org/document/656776}  } & 
Ablex Publishers, New Jersey        & 
1996 \\ \hline
2       & C.P. Ravikumar (Ed). & VLSI Design and Test – Milestones and Challenges& Phoenix Publishers. New Delhi & 2000  \\ \hline
3       & C.P. Ravikumar (Ed). & Frontiers of VLSI Design and Test & Phoenix Publishers, New Delhi    & 2001\\ \hline
4       & C.P. Ravikumar (Ed). & Progress in VLSI Design and Test & Phoenix Publishers, New Delhi       & 2002\\ \hline
5       & C.P. Ravikumar (Ed). & Progress in VLSI Design and Test 2003 & Elite Publishing House, New Delhi      & 2003 \
\\ \hline
6       & C.P. Ravikumar et al. (Ed). & New Frontiers in High Performance Computing     & Elite Publishing House, New De
lhi     & 2003\\ \hline
7       & C.P. Ravikumar (Ed). & Progress in VLSI Design and Test 2004.         & Elite Publishing House, New Delhi
2004\\\hline
8       & C.P. Ravikumar (Ed). & Progress in VLSI Design and Test 2005.         & Elite Publishing House, New Delhi & 2005\\\hline
9       & C.P. Ravikumar (Ed). & Progress in VLSI Design and Test 2006.         & Elite Publishing House, New Delhi & 2006\\\hline
10      & Susmita Sur-Kolay, D. Mukhopadhyay, and C.P. Ravikumar (Ed). & Progress in VLSI Design and Test 2007.
& Elite Publishing House, New Delhi     & 2007\\\hline
11      & Shabbir Batterywala and C.P. Ravikumar (Ed). & Progress in VLSI Design and Test 2008.         & Elite Publishi
ng House, New Delhi     & 2008\\\hline
12      & C.P. Ravikumar (Ed). & Progress in VLSI Design and Test 2009.         & Elite Publishing House, New Delhi
& 2009\\\hline
13      & K.R.K. Rao and C.P. Ravikumar, & “Analog System Lab Manual”   & Wiley India, New Delhi        & 2011\\\hline
14      & C.P. Ravikumar & Progress in VLSI Design and Test.  Proceedings of VLSI Design and Test Symposium (2010) & Chitkara University Press, Chandigarh   & 2011\\\hline
15      & C.P. Ravikumar (Ed.) & MSP430 Microcontroller in Embedded System Projects.    & Elite Publishing House, New Delhi     & 2011\\\hline
16      & C.P. Ravikumar (Ed.) & Innovative Electronic System Design Projects. & Chitkara University Press, Chandigarh. & 2014\\\hline
\end{longtable}

\section*{Book Chapters}
\begin{enumerate}
\item   Contributed Chapter 9 to the book “Low Power VLSI Test” edited by P. Girard, X. Wen, and N. Nicolici. Springer P
ublishers (2009).
\item   Contributed Chapter 1 to the book “Multi-core Embedded Systems” edited by Georgios Kornaros. CRC Press (2010).
\end{enumerate}

\section*{Technical Reports}
\begin{enumerate}
\item   D.-H. Heo, C.P. Ravikumar and A. Parker.  Versatile Multichip Digital System Architecture Synthesis Tools.  Tech
 Report 96-26. Department of EE-Systems, University of Southern California, Los Angeles, October 1996.
\item   D.-H. Heo, C.P. Ravikumar and A. Parker.  Rapid Synthesis of Multichip Systems.  Tech Report 96-25. Department o
f EE-Systems, University of Southern California, Los Angeles, October 1996.

\end{enumerate}

\section*{Edited}
\begin{itemize}
\item   Editor of VSI VISION – Periodical of the VLSI Society of India (since its inception to 2010).
\footnote{
These are archived at Research Gate e.g. see \url{https://www.researchgate.net/publication/261879381_VSI_VISION_-_Vol_1_Issue_1_Newsletter_of_VLSI_Society_of_India
}
}
\item   Editor of UniTI Newsletter – Periodical of the TI India University Program (since its inception in 2008 to prese
nt)
\footnote{
These are archived at Research Gate e.g. see \url{https://www.researchgate.net/publication/261879466_UniTI_Newsletter_-_Newsletter_of_TI_India_University_Program_-_Vol_2_Issue_3}
}
\end{itemize}

\section*{Lab or Design Manuals}
\begin{itemize}
\item   C.P. Ravikumar, Editor, Laboratory manual for Computer Technology Lab and Software Labs. Department of Electrica
l Engineering, IIT Delhi. 1995.
\item   C.P. Ravikumar. Instructional Software for teaching Computer Architecture. CD-Cell, IIT Delhi, 1995.
Kannada Publications
\item   C.P. Ravikumar. Computer-gondu Kannadi. In Kannada. Collection of essays written in Kannada on various current t
opics related to computers. Published in 1997 by Abhinava Publishers, Bangalore.
\item   C.P. Ravikumar. Information Processing and Information Systems.  Book chapter in Kannada language, to appear in
the Encyclopedia  compiled by Dr. T.S. Satyanath for the Hampi University, Karnataka.
\item   C.P. Ravikumar.  Multimedia Information Systems. In H. S. Raghavendra Rao, editor, Adhyayana, pages 28--34. Hamp
i University, India, 1994.
\item C.P. Ravikumar, Punarnava, Novel, Abhinava Publishers, 2022.
\end{itemize}

\section*{Unpublished}
\begin{itemize}
\item Introduction to Information Technology (in Kannada). Completed in 2002 and revised in 2020.
\item Translation of Children's Book "The Conch Bearer", completed in 2024.
\end{itemize}
\end{document}
